Place of death in NRS COVID-19 deaths: data processing for analysis

### 2021-08-19 covid_nrs_place_of_death_data.Rmd
slight format change in the weekly deaths spreadsheet caused an error due to mismatch in number of expected and actual columns in 2021 data, so I hacked up a solution

## construct column names for the data
headers_in_nrs_data_2020 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0("week_", 1:53),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1",
    "remove_2"
  )
headers_in_nrs_data_2021 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0(
      "week_",
      1:weeks_available_in_nrs_weekly_data_by_cause_of_death_2021
    ),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1"
  )

>>>>

## construct column names for the data
headers_in_nrs_data_2020 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0("week_", 1:53),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1",
    "remove_2"
  )
headers_in_nrs_data_2021 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0(
      "week_",
      1:weeks_available_in_nrs_weekly_data_by_cause_of_death_2021
    ),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1"
  )
## in week 32 of 2021, the format changed somewhat and the blank column in penultimate location in Table 3 (2021) was removed
## so this is a hack that gets around that!
expected_ncol_2021 <- length(headers_in_nrs_data_2021)
actual_ncol_2021 <- ncol(readxl::read_excel(files_weekly_deaths$main_report, sheet = nrs_weekly_data_sheet_2021))
headers_in_nrs_data_2021 <- headers_in_nrs_data_2021[1:actual_ncol_2021]  # subset the first N of the defined headers, where N is actual number of columns in file
